DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
Editing Sec III

In step $1$, the user has to define the digital controller representation, 
which can be a transfer function or a state-space model. 
In step $2$, the physical plant (represented by Equations (\ref{eq:transferfunction}) 
and (\ref{eq:ss-example})) must be designed, using a method selected 
from the control literature~\cite{astrom1997computer}. Finally, in step $3$, 
the numerical representation for the digital controller implementation must be 
defined by the user, {\it i.e.}, the FWL format that includes the number of bits for the integer 
and fractional parts as well as the dynamic range inputs. The result of the manual 
procedure performed by the user is a digital system specification for the given 
physical plant in MATLAB.

After that, the synthesis process starts in step $A$, when \tool obtains the digital system 
specification in MATLAB, and then translates it into an ANSI-C program. 
In step $B$, our CEGIS engine is invoked to synthesize the digital controller w.r.t. the digital system
specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
The output generated by \tool is the synthesized digital controller represented either in transfer function 
or state-space equation. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
synthesized w.r.t. FWL effects; otherwise, if any parameter is incorrectly defined in previous steps, 
or if there is no solution (digital controller) for the respective physical plant (given the digital controller
 implementation aspects), then the synthesis is considered to be \emph{failed}.

Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
transforms an ANSI-C representation of our closed-loop control system model into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume} intrinsic functions).  Our module was included in CBMC~5.7 and is available for
public download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\.footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
of our tool is available in a public GitHub
repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}

>>>>

In step $1$, the user has to define the digital controller representation, 
which can be a transfer function or a state-space model. 
In step $2$, the physical plant (represented by Equations (\ref{eq:transferfunction}) 
or (\ref{eq:ss-example})) must be designed, using a method selected 
from the control literature~\cite{astrom1997computer}. Finally, in step $3$, 
the numerical representation for the digital controller implementation must be 
defined by the user, {\it i.e.}, the FWL format that includes the number of bits for the integer 
and fractional parts as well as the dynamic range inputs. The result of the manual 
procedure performed by the user is a digital system specification for the given 
physical plant in MATLAB.

After that, the synthesis process starts in step $A$, when \tool obtains the digital system 
specification in MATLAB, and then translates it into an ANSI-C program. 
In step $B$, our CEGIS engine is invoked to synthesize the digital controller w.r.t. the digital system
specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
The output generated by \tool is the synthesized digital controller represented either in transfer function 
or state-space equation. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
synthesized w.r.t. FWL effects; otherwise, if any parameter is incorrectly defined in previous steps, 
or if there is no solution (digital controller) for the respective physical plant (given the digital controller
 implementation aspects), then the synthesis is considered to have \emph{failed}.

Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
transforms the ANSI-C representation of our closed-loop control system model into its internal format called
\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume} intrinsic functions).  Our module was included in CBMC~5.7 and is available for
public download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}  We further created a VirtualBox OVA image
with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
to run all benchmarks and reproduce our
experiments\.footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
of our tool is available in a public GitHub
repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}
